Handwritten Digit Recognition Using Deep Convolutional Neural Network*

### 2022-04-28 paper/paper.tex
minor fixes

As such, our neural network (Figure \ref{fig:cnn_architecture}) starts with a rescaling layer, which is nothing but normalizing the grayscale values from $[0, 255]$ to $[0, 1]$. It is then followed by a 2D convolutional layer with $28 \, 3 \times 3$ kernels, outputting 28 feature maps. The feature maps are then pooled with a $2 \times 2$ pool--size max pooling layer, cutting the amount of pixels in each feature map by $4$. We then apply batch normalization\cite{batchnorm} to reduce overfitting, and redo the above process once more before flattening the image.\@

@@

As mentioned earlier, no preprocessing was done to the images, and for normalizing the pixel values to the $[0, 1]$ range, there is a rescaling/normalization layer at the forefront of the DCNN. The only thing in our data pipeline was an autotune prefetch and batching to $128$ images per patch, neither effect the images but have an effect on loading the images into memory (RAM), that was done to speed up the training process

@@

That is to say that training stops once it plateaus (with 5 epochs and no improvement), and that the best performing model (in terms of validation loss)is saved, which is later loaded and used for the predictions.\@ 

@@

With the architecture described in Section \ref{sec:cnn} and even our cheap, widely available specifications, training took merely a minute, and the per--epoch progress is shown in Figure \ref{fig:perepoch}

@@

In conclusion, we believe that DCNNs have an important role in upcoming OCR technologies.\@ The results of our experiment are phenomonal, near--human accurate, and with very little cost in terms of time spent on developing the model, training the model, and the price of the hardware used.\@

>>>>

As such, the neural network (Figure \ref{fig:cnn_architecture}) starts with a rescaling layer, which is nothing but normalizing the grayscale values from $[0, 255]$ to $[0, 1]$. It is then followed by a 2D convolutional layer with $28 \, 3 \times 3$ kernels, outputting 28 feature maps. The feature maps are then pooled with a $2 \times 2$ pool--size max pooling layer, cutting the amount of pixels in each feature map by $4$. We then apply batch normalization\cite{batchnorm} to reduce overfitting, and redo the above process once more before flattening the image.\@

@@

As mentioned earlier, no preprocessing was done to the images, and for normalizing the pixel values to the $[0, 1]$ range, there is a rescaling/normalization layer at the forefront of the DCNN. The only process in the data pipeline was an autotune prefetch and batching to $128$ images per patch, neither effect the images but have an effect on loading the images into memory (RAM), that was done to speed up the training process

@@

That is to say that training stops once it plateaus (with 5 epochs and no improvement), and that the best performing model (in terms of validation loss) is saved, which is later loaded and used for the predictions.\@ 

@@

The training ran for 9 epochs before being stopped with the \verb|EarlyStopping| callback. With the architecture described in Section \ref{sec:cnn} and the cheap, widely available specifications, training took merely a minute, and the per--epoch progress is shown in Figure \ref{fig:perepoch}

@@

In conclusion, we believe that DCNNs have an important role in upcoming OCR technologies.\@ The results of the experiment are phenomonal, near--human accurate, and with very little cost in terms of time spent on developing the model, training the model, and the price of the hardware used.\@
